---
title: "NOpitz_DSC630_Final_Project_R_Code"
author: "Neil Opitz"
date: "11/20/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## R Markdown


```{r libraries}
library(e1071) 
library(caTools) 
library(caret) 
library(ggplot2)
```


## Import Data


```{r import data}
# import data
all_data <- read.csv('dsc630final_all_sources.csv')
cal_data <- read.csv('dsc630final_california.csv')
```


### Model 1
#### All Data
#### Linear Regression
#### Explanatory = Percent Energy Production
#### Response = Percent Unhealthy Days


```{r model 1}
# Linear Model - All Data

linear_all <- lm(Percent_Unhealthy_Days ~ green_percent + Natural_Gas_Percent + 
                Coal_Percent + Petroleum_Percent, data=all_data) 

summary(linear_all)
```


### Model 2
#### All Data
#### Logistic Regression
#### Explanatory = Raw Energy Production
#### Response = Binary Median AQI


```{r model 2}

# Logistic Model - All Data

# Splitting data into train and test data 
set.seed(101)
sample <- sample.int(n = nrow(all_data), size = floor(.70*nrow(all_data)), replace = F)
all_train <- all_data[sample, ]
all_test  <- all_data[sample, ]

classifier <- glm(AQI_GT38 ~ TOTAL_GREEN_PRODUCTION + Coal + Natural_Gas
                  + Petroleum, data = all_train) 

summary(classifier)

# predict outcome on test dataset
prob_pred <- predict(classifier, type = 'response', newdata = all_test[])

# transform prob_pred into 0 and 1 results
y_pred <- ifelse(prob_pred > 0.5, 1, 0)

# make confusion matrix
cm <- table(all_test[,36], y_pred)

# calculate accuracy
accuracy <- (cm[1,1] + cm[2,2]) / (cm[1,2] + cm[2,1]+ cm[1,1] + cm[2,2])
accuracy
```


### Model 3
#### California Data
#### Linear Regression
#### Explanatory = Raw Energy Production + Wildfire Acres Burned
#### Response = Percent Unhealthy Days


```{r model 3}
# Linear Model - California Data

linear_cal <- lm(Percent_Unhealthy_Days ~ Natural_Gas_Percent + Petroleum_Percent + Coal_Percent +
                   Hydroelectric_Conventional_Percent + Wood_Wood_Derived_Fuels_Percent + 
                   Wind_Percent + Nuclear_Percent + Solar_Thermal_Photovoltaic_Percent +
                   Pumped_Storage_Percent + Geothermal_Percent + Other_Biomass_Percent +
                   Other_Percent + ACRES_BURNED, data=cal_data) 

summary(linear_cal)
```


### Model 4
#### All Data
#### Linear Regression
#### Explanatory = Percent Green Energy Production
#### Response = Median AQI



```{r model 4}
# AQI LINEAR MODEL

linear_all_aqi <- lm(Median.AQI ~ green_percent, data=all_data) 

summary(linear_all_aqi)
```











